Models of Lambek calculus enriched with subexponentials

### 2019-03-13 PaperDraft.tex
update

\begin{defin}
  Let $W$ be a set. A Kripke frame is a pair $\mathcal{W} = \langle W, R, I \rangle$,
  where $R$ is a ternary relation on $W$ and $I$ is an unary relation on $W$.

@@

  \begin{enumerate}
    \item $\mathcal{W}, w \Vdash p_i \Leftrightarrow w \in v(p_i)$;
    \item $\mathcal{W}, w \Vdash {\bf 1} \Leftrightarrow I(w)$;
    \item $\mathcal{W}, w \Vdash A \bullet B \Leftrightarrow \exists u, v \in W, R(u,v,w) \text{ and } \mathcal{W}, u \Vdash A \text{ and } \mathcal{W}, v \Vdash B$;
    \item $\mathcal{W}, w \Vdash A \backslash B \Leftrightarrow \forall u, v \in W, R(u,w,v) \text{ and } \mathcal{W}, u \Vdash A \text{ implies } \mathcal{W}, v \Vdash B$;
    \item $\mathcal{W}, w \Vdash B / A \Leftrightarrow \forall u, v \in W, R(w,u,v) \text{ and } \mathcal{W}, u \Vdash A \text{ implies } \mathcal{W}, v \Vdash B$;
    \item $\mathcal{W}, w \Vdash A \lor B \Leftrightarrow \forall u, v \in W, R(u,v,w) \text{ either } \mathcal{W}, u \Vdash A \text{ or } \mathcal{W}, v \Vdash B$;
    \item $\mathcal{W}, w \Vdash A \land B \Leftrightarrow \mathcal{W}, w \Vdash A \text{ and } \mathcal{W}, w \Vdash A$;
    \item $\mathcal{W}, w \Vdash \Gamma \rightarrow A \Leftrightarrow \mathcal{W}, w \Vdash \bullet \Gamma \text{ implies } \mathcal{W}, w \Vdash A$.
  \end{enumerate}
\end{defin}

@@

@@

>>>>

\begin{defin}
  Let $W$ be a set. A Kripke frame is a 3-tuple $\mathcal{W} = \langle W, R, I \rangle$,
  where $R$ is a ternary relation on $W$ and $I$ is an unary relation on $W$.

@@

  \begin{enumerate}
    \item $\mathcal{M}, w \Vdash p_i \Leftrightarrow w \in v(p_i)$;
    \item $\mathcal{M}, w \Vdash {\bf 1} \Leftrightarrow I(w)$;
    \item $\mathcal{M}, w \Vdash A \bullet B \Leftrightarrow \exists u, v \in W, R(u,v,w) \text{ and } \mathcal{W}, u \Vdash A \text{ and } \mathcal{W}, v \Vdash B$;
    \item $\mathcal{M}, w \Vdash A \backslash B \Leftrightarrow \forall u, v \in W, R(u,w,v) \text{ and } \mathcal{W}, u \Vdash A \text{ implies } \mathcal{W}, v \Vdash B$;
    \item $\mathcal{M}, w \Vdash B / A \Leftrightarrow \forall u, v \in W, R(w,u,v) \text{ and } \mathcal{W}, u \Vdash A \text{ implies } \mathcal{W}, v \Vdash B$;
    \item $\mathcal{M}, w \Vdash A \lor B \Leftrightarrow \forall u, v \in W, R(u,v,w) \text{ either } \mathcal{W}, u \Vdash A \text{ or } \mathcal{W}, v \Vdash B$;
    \item $\mathcal{M}, w \Vdash A \land B \Leftrightarrow \mathcal{W}, w \Vdash A \text{ and } \mathcal{W}, w \Vdash A$;
    \item $\mathcal{M}, w \Vdash \Gamma \rightarrow A \Leftrightarrow \mathcal{W}, w \Vdash \bullet \Gamma \text{ implies } \mathcal{W}, w \Vdash A$.
  \end{enumerate}
\end{defin}

@@

\begin{proof}
\end{proof}

\begin{defin}
  Mininal normal modal Lambek calculus is $L^{*}_{\bf 1} \land \lor$ with additional rule:

  \begin{prooftree}
    \AxiomC{$\Gamma \rightarrow A$}
    \UnaryInfC{$!\Gamma \rightarrow !A$}
  \end{prooftree}
\end{defin}

@@

\begin{defin}
  A modal Kripke frame is a 4-tuple $\mathcal{W}_{!} = \langle W, R, Q, I \rangle$, where $Q$ is a preorder on $W$,
  a Kripke model is tuple $\mathcal{M} \langle \mathcal{W}_{!}, v \rangle$. A forcing relation for $!$ is defined as follows:
  \item $\mathcal{M}, w \Vdash !A \Leftrightarrow \forall v, Q(w, v) \Rightarrow \mathcal{W}, v \Vdash A$;
\end{defin}

  Let $\mathbb{F}$ be a class of modal Kripke frames, then $Log(\mathbb{F}) = {L^{*}_{\bf 1} \land \lor}_{\bf S4}$.
\end{theorem}

  $\Gamma \models A$, then ${L^{*}_{\bf 1} \land \lor}_{\bf S4} \vdash \Gamma \rightarrow A$
\end{proof}
